\documentclass[9pt,a4paper]{extarticle}

\usepackage[a4paper,margin=1.2cm]{geometry}
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage{lmodern}
\usepackage{xcolor}
\usepackage[hidelinks]{hyperref}
\usepackage{enumitem}

\pagestyle{empty}
\setlength{\parindent}{0pt}
\setlength{\parskip}{1pt}
\setlist[itemize]{leftmargin=12pt,itemsep=0pt,topsep=1pt,parsep=0pt,partopsep=0pt}

\definecolor{heading}{HTML}{1F2937}
\definecolor{textsoft}{HTML}{4B5563}

\newcommand{\sectiontitle}[1]{%
  \vspace{3pt}
  {\small\bfseries\color{heading}#1}\par
  \rule{\linewidth}{0.35pt}\vspace{1pt}
}

\newcommand{\roleheader}[3]{%
  {\bfseries #1} \hfill {\color{textsoft}#2}\\[-1pt]
  {\itshape #3\/}\\[-2pt]
}

\begin{document}

{\Large\bfseries Eduardo Meireles Lopes}\\[-1pt]
{\normalsize Software Engineer | Product Engineer}\\[-1pt]
Mafra / Lisbon, Portugal \textbar\ \href{mailto:eduardofilipelml@gmail.com}{eduardofilipelml@gmail.com} \textbar\ \href{https://www.linkedin.com/in/eduardomeireleslopes/}{linkedin.com/in/eduardomeireleslopes}\\
\href{https://github.com/eduardofilipelml}{github.com/eduardofilipelml} \textbar\ \href{https://eduardofilipelml.github.io/}{eduardofilipelml.github.io}

\sectiontitle{Professional Summary}
Software Engineer with 8+ years of experience building enterprise software across fintech, space technology and web applications. Experienced in designing reliable, maintainable systems spanning desktop, backend integrations and modern web interfaces, with a pragmatic approach to AI-assisted software development.

\sectiontitle{Technical Skills}
\textbf{Core Engineering:} Java, Swing, Eclipse RCP, Spring, C++, XML\\
\textbf{Web Engineering:} JavaScript, React, Vite, HTML, CSS\\
\textbf{Testing and Quality:} JUnit, QF-Test, test automation, regression testing\\
\textbf{DevOps and Workflow:} Git, CI/CD, Podman, Agile delivery\\
\textbf{AI-assisted Engineering:} GitHub Copilot, ChatGPT, Cursor, Claude Code

\sectiontitle{Professional Experience}
\roleheader{Software Developer, Profidata AG}{2021 \textendash{} Present}{Fintech product engineering}
\begin{itemize}
  \item Delivered and evolved core Xentis modules supporting portfolio operations, compliance workflows, and fund administration in regulated financial contexts.
  \item Expanded automated regression and UI coverage, increasing release confidence while reducing manual validation effort.
\end{itemize}

\roleheader{Software Engineer, Deimos Engenharia}{2017 \textendash{} 2021}{ESA Earth Observation software}
\begin{itemize}
  \item Delivered engineering contributions to ESA Earth Observation applications including S2G, ESOV, and DFDL4S.
  \item Built and evolved Java desktop tooling that improved telemetry visualization and technical data inspection workflows.
\end{itemize}

\roleheader{Freelance Web Developer, Independent Projects}{2025 \textendash{} Present}{Client web delivery}
\begin{itemize}
  \item Delivered custom websites for small businesses from requirements gathering to release.
  \item Built responsive interfaces that improved readability, maintainability, and overall delivery quality.
\end{itemize}

\sectiontitle{Selected Projects}
\textbf{Xentis Investment Management (CURRENT)} \textendash{} Enterprise platform for portfolio management, compliance, and fund administration.\\
\textbf{ESA Tooling (ESOV, DFDL4S, S2G)} \textendash{} Java desktop and data tooling for mission analysis and telemetry workflows.\\
\textbf{Web Delivery Portfolio (WEB)} \textendash{} Business websites with responsive UX and maintainable frontend structure.

\sectiontitle{Education}
\textbf{Master in Computer Science}, FCT-UNL \hfill 2015 \textendash{} 2020\\
Focus areas: web development, data analysis, machine learning, and visualization.\\[-1pt]
\textbf{Bachelor in Computer Science}, FCT-UNL \hfill 2010 \textendash{} 2015\\
Core training in software engineering, algorithms, and object-oriented programming.

\sectiontitle{Languages}
Portuguese (Native), English (Professional working proficiency), Spanish (Beginner)

\end{document}
